\documentclass[letterpaper,11pt]{texMemo}

\usepackage{graphicx}

%\memotitle{Memorandum}
\memoto{Roby Conner, Writing 327 Instructor}
\memofrom{Jacques Uber, Oregon State University Student}
\memodate{Feb 12, 2012}
\memosubject{Proposal to investigate imporovements to Tor}
\memologo{Memorandum}

\begin{document}
\maketitle

\section{Introduction}

I will investigate how engineers are working to improve Tor. Specifically, I will focus on the
improvements to latency and congestion, and the methods used to improve user anonymity.

Scope – Use the following statement and fill in the blanks with your
information

    The literature review will include all scholarly articles on Tor found via the Academic Search
    Premier database using the keywords Tor, Improvements, Congestion, Fair, Timing Attacks,
    Anonymity and published between the years 2009 and 2012.

    There will be three section in the document. The first section will introduce core concepts used
    to implement Tor. The second will investigate techniques used to compromise user
    anonymity. The third will investigate network latency and congestion.

\section{Background}

    o The bulk of your research will go here to explain the context, significance,
    and source of the problem you intend to research. You must cite all
    information taken from your research.
    

    o Discuss history of the problem/topic

    o Demonstrate the need for the research
    Research Plan

    o The literature review will address the following research questions. Restate
    them to reflect your specific topic.

         What trends in research methods or results can be identified in the
        literature?

         Are there identifiable controversies within the literature?

         Are there identifiable weaknesses in the methods or conclusions in the
        literature?

         What areas/topics for future research are recommended in the
        literature?

    o Minimum of six (6) sources (peer-reviewed articles from academic, trade, or
    scientific journals)

         Include a brief description of each article (Title, author, topic)

         1-2 sentences should describe why the article is included

\section{Research Plan}
Conclusion
    o Summary of Key Points

    o Request for Action/Approval
    Works Cited Page (MLA formatted)

\end{document}
